---
title: "MA677_HW1"
author: "Haoqi Wang"
date: "2/11/2021"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
```


## Experiments
In our hypothesis test, the null hypothesis is that: $H_0:P=0.6$ and the alternative hypothesis is that: $H_1:P>0.6$. The Type I error refers to reject the null hypothesis when in fact it is true. And $\alpha(p)$ is the probability of type 1 error. Whereas $\beta(p)$ is the probability of the type 2 error, which is to accept the null hypothesis when it is false.
In this case, choosing m well below np = .8n will increase $\alpha(.8)$, since now $\alpha(.8)$ is all but the lower tail of a binomial distribution. Indeed, if we put $\beta(.8)$ = 1 − $\alpha(.8)$, then $\beta(.8)$ gives us the probability of a type 2 error, and so decreasing m makes a type 2 error less likely. So we should make the probabilities of each type error less than 0.05. So we know:
$$\alpha(p)=\sum_{m\le{k}\le{n}}b(n,p,k)=\sum_{60\le{k}\le{100}}b(100,0.6,k)$$

 $$\beta(p)=1-\alpha(p)=\sum_{k\le{m}}b(n,p,k)=\sum_{k\le{80}}b(100,0.8,k)$$
```{r,warning=FALSE}
#type 1 error when p=0.6
n=100
p=0.6
t=100-n*p
m1=rep(0,t)
p1=rep(0,t)
for(i in 0:t){
  m1[i]=i+n*p
  p1[i]=pbinom(n,n,p)-pbinom(m1[i]-1,n,p)
}
a=data.frame(cbind(m1,p1))
```


```{r}
#type 2 error when p=0.8
n=100
p=0.8
t=100-n*p
m2=rep(0,t)
p2=rep(0,t)
for(i in 0:t){
  m2[i]=n*p-i
  p2[i]=pbinom(m2[i]-1,n,p)
}
b=data.frame(cbind(m2,p2))
```

```{r}
a1 <- a[which(a$p1<0.05),1]
b1 <- b[which(b$p2<0.05),1]
```

The minimum value is:
```{r,echo=FALSE}
print(min(a1))
```
The maximum value is:
```{r,echo=FALSE}
print(max(b1))
```

### Figure 3.7

```{r}
n = 100
p = seq(from=0.4,to=1,by=0.01)
P69=cumsum(dbinom(min(a1),n,p))
P73=cumsum(dbinom(max(b1),n,p))
dt=data.frame(p,P69,P73)
ggplot(dt)+
  geom_segment(aes(x=0.6,xend=0.8,y=0.95,yend=0.95),colour="black")+
  geom_segment(aes(x=0.6,xend=0.8,y=0.05,yend=0.05),colour="black")+
  geom_segment(aes(x=0.6,xend=0.6,y=0.05,yend=0.95),colour="black")+
  geom_segment(aes(x=0.8,xend=0.8,y=0.05,yend=0.95),colour="black")+
  geom_line(aes(p, P69),color="blue")+
  geom_line(aes(p, P73),color="red")+
  xlab("p") +
  ylab("a(p)") +
  ggtitle("The power curve") 
  
```

#